On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-12 Manuscript/manuscript.tex
Left some comments, may need to go through again

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h$, the standard deviation of the venue effect
is $\sigma_v$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
square root of the dispersion parameter $\phi$.
The GLMM with both venue and heat random effects was the best model as evidenced
by a decrease in the AIC compared to the other models with only one random
effect.  When we exclude 2022 from the full model, we observe small but intriguing
discrepancies in the models. The standard deviation of the venue effect, 
$\sigma_v$, decreases from 0.40 to 0.33 when 2022 is excluded.  Thus, 2022
increased the noise in the overall data and confirms that it is an outlier.

@@

Figure~\ref{fig:VenueEffects} shows the venue effects from 1999 to 2023 based
on the full model both with and without 2022.  As this graph does not show heat
\jy{discuss the years the venue effects are high and low}
effects, the estimates may not align exactly with the box plot presented in
figure~\ref{fig:Boxplot}.  The venue effect for 2022 is lower than any other
effect, confirming that 2022 was a low outlier. \jy{but may not be as extreme as
  one would think considering the whole history.}

\jy{Hopefully, the full model is preferred for both with and without 2022}

>>>>

\jy{Hopefully, the full model is preferred for both with and without 2022}
\of{It is but the AIC are more similar without 2022}

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h$, the standard deviation of the venue effect
is $\sigma_v$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
square root of the dispersion parameter $\phi$.
The GLMM with both venue and heat random effects was the best model as evidenced
by a decrease in the AIC compared to the other models with only one random
effect.  When we exclude 2022 from the full model, we observe small but intriguing
discrepancies in the models. The standard deviation of the venue effect, 
$\sigma_v$, decreases from 0.40 to 0.33 when 2022 is excluded.  Thus, 2022
increased the noise in the overall data, but many of the other statistics
remained relatively similar, such as the standard deviation of the heat effect
and the dispersion parameter.

%\of{Can I just refer to it as the dispersion parameter or should I say "square
%root of the dispersion parameter" Mathematically it shouldn't make a difference 
%right as 0.134^2 and 0.136^2 are very similar and I am applying a function to 
%both? Also should I be saying "standard deviation of heat effect", or sigma_v 
%or both?}

@@

Figure~\ref{fig:VenueEffects} shows the venue effects from 1999 to 2023 based
on the full model both with and without 2022.  As this graph does not show heat
\jy{discuss the years the venue effects are high and low}
effects, the estimates may not align exactly with the box plot presented in
figure~\ref{fig:Boxplot}.  The venue effect for 2022 is lower than any other
effect, but may not be as extreme as one would think considering the history
of reaction times going back to 1999.
